The group for this project consists of four out of five members from the P1 group. During the initial stages of the group work we signed a group contract, which was a revised one from our previous project.\\
We attempted to distribute the workloads evenly, so that everyone had the same amount of contribution to the project.\\
Outside of the scheduled group meetings we participated in different events and social activities together, to get to know each other better on a personal level.
\section{Discussion and Conclusion}

%the whole thing with motivation
The project was off to a slow start after the winter break, because of the vacation. We then quite easily figured out what we would like the subject of the project to be, which then started the preliminary research.\\
During the preliminary research a large conflict arose in relation to motivation. Two out of the four group members considered at the time dropping out of the studies, which slowed down the progression of the project tremendously. After some talks back and forward the supervisors we all came to a mutual agreement. We then created a secondary group contract labelled the "Deadline contract". This contract was put into place to ensure that the members of the group fulfilled the tasks that was expected from them.\\
The group the returned to a well functioning state and things started flowing. Towards the end of the project, during the development, we realized that out scope was too big compared to what we were able to accomplish. Many man hours and nights were spent on getting the core of our  prototype to work. All of the setbacks from the development resulted in less time for the remaining part of the report. During the final two weeks of the project we all worked really hard every single day with new deadlines, to ensure that our project was done on time.\\
Besides minor disagreements on different decisions throughout the whole project and the whole dispute in relation to motivation, there were no major conflicts in the group.

We stuck together when times got tough, during the initial stages and the final stages of the project, and we believe that the next project will be even better.