Why we need to explore other unknown terrains is to help us better understand everything around us and to be able to go to other planets. If we are flying in the dark about the terrain underwater or on another planet and we are planning of settling there or use those resources then we have a bigger change of failure. If the trips are planned well and we make a good 3D map of the terrain we can come up with better plans on the next mission or if we want to use this location at all. 

The problems with navigating a robot in an unknown terrain is the lack of reference points that are needed to make a 3D map and also reference point for the robot itself to being able to navigate. That makes two challenges for us. One is for the robot to being able to navigate through a completely unknown terrain and at the same time make sense of it and come up with reference point that will be use to make a 3D map.

If a robot is successful with that task and we get back a detailed 3D map then the next mission can rely on that information and have a easier way to navigate. 

On earth we have the GPS (global positioning system) that is an space based satellites navigation system flying over the earth [reference: http://www.loc.gov/rr/scitech/mysteries/global.html]. But putting up a system like that on another planet cost a lot of resources and the cost to start with would not be beneficial. GPS also does not penetrate water [reference: http://www.newscientist.com/blog/invention/2007/03/underwater-gps.html]. 

% More detailed description of GPS and reference points will the in the theory part //need to have this ?

% ------------------------------------------ Links for Emil ---------------------------------

% Good talk about making 3D maps on Mars

% http://content.stamen.com/how_to_make_3d_maps_of_mars

% Ultra sharp 3D maps

% http://video.mit.edu/watch/ultrasharp-3-d-maps-66/

% GPS links

% http://en.wikipedia.org/wiki/Global_Positioning_System

% http://www.gps.gov/systems/gps/space/

% http://spectrum.ieee.org/aerospace/space-flight/interplanetary-gps-comes-a-step-closer

% http://science.howstuffworks.com/how-is-gps-used-in-spaceflight.htm

% ---------------------------------- Old text -----------------------------------------

% Why should we solve this problem? Why is this a problem?

% Exploration of unknown planetary terrain will be heavily needed in the future in the search for other lifeforms, by creating a device that remotely can map and record data about the terrain, the terrain can be analysed before an expedition is started. This will save a lot of money and also rule out some unknown areas without the need for an entire expedition.

% Unknown terrain is an issue, since there are possibilities for GPS. This makes it hard for regular exploration vehicles to map and explore the area, since it's impossible for the vehicle to efficiently create a reference point.

% Unknown terrain is also an issue when it comes to manned expeditions, since there are no maps or data recordings from the

% Talk about a side note what is used instead of gps and how that technology could perhaps help us

% We need detailed maps of the places we will visit in outer space so we can plan better for a return to that place. Make plans to send other robots or even colonize it.
